Robust Spectroscopic Inference with Imperfect Models

### 2014-11-04 tex/paper.tex
More figure tweaks

\capstartfalse
\begin{deluxetable}{lr@{ $\pm$ }l|r@{ $\pm$ }l}[!b]
\tablecaption{\label{table:Kurucz}Inferred Parameters for WASP-14}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{{\sc CfA/Kurucz}} & \multicolumn{2}{c}{{\sc Phoenix}}}
\startdata
$T_{\rm eff}$ (K) & 6424     & 19                      &  6354   & 39        \\
$\log g$      & 4.29     & 0 (fixed)               &  4.29   & 0 (fixed) \\
$\Z$          & -0.26    & 0.01                    & -0.30  & 0.02     \\
$v \sin i$ ($\kms$)\tablenotemark{a}   & 4.47 & 0.06       &  5.09   & 0.06      \\
$v_z$ ($\kms$)        & -4.60    & 0.02                    & -4.86   & 0.02      \\
$\log \Omega$\tablenotemark{b} & -12.7180 & 0.0004 & -12.717 & 0.0007 \\
$A_V$                          & 0        & 0 (fixed) & 0 & 0 (fixed)
\enddata
\tablenotetext{a}{Small differences in the rotational broadening between the two libraries are
expected, since they assume different micro- and macro-turbulence behavior in the stellar
atmospheres.}
\tablenotetext{b}{For the spectral emulator (Appendix~\ref{sec:Appendix}), the models are scaled to 
an average flux of unity, rather than flux at the stellar surface; the quoted values are unknown 
multiples of $R^2/d^2$.}
\tablecomments{The quoted values represent the ``best-fit", the peak of the marginal posterior 
distributions for each parameter.  The quoted uncertainties correspond to the 68.3\%\ 
($\sim$1\,$\sigma$) confidence intervals.  Expanded lists of the inferred values and uncertainties 
for all nuisance parameters are available electronically.}
\end{deluxetable}
\capstarttrue

@@

\begin{figure*}[!t]
  \begin{center}
  \includegraphics{figs/pca_reconstruct.pdf}
  \vspace{-0.6cm}
  \figcaption{ (\emph{top}) The mean spectrum, standard deviation spectrum, and five eigenspectra 
that form the basis of the \textsc{Phoenix} synthetic library used to model Gl~51, generated using 
a subset of the parameter-space most relevant for M dwarfs.  (\emph{bottom}) The original synthetic 
spectrum from the \textsc{Phoenix} library compared with a spectrum reconstructed from a linear 
combination of the derived eigenspectra using Eqn~\ref{eqn:reconstruct} (with the weights $w_k$ 
listed in the top panel figure).  \label{fig:pca_reconstruct}}
  \end{center}
\end{figure*}

@@

Now the Gaussian process is fully specified and can be used to predict the values of the weights at 
any arbitrary set of stellar parameters $\vt_\ast$ by considering them drawn from the joint 
distribution 
\begin{equation}
  \begin{bmatrix}
    \mathbf{w}_k^\textrm{grid}\\
    w_k
  \end{bmatrix} \sim
  \mathcal{N} \left (
  \mathbf{0},
  \begin{bmatrix}
  \mathbf{\Sigma}_k^\textrm{grid} & \mathcal{K}( \{\vt_\ast \}^\textrm{grid}, \vt_\ast) \\
  \mathcal{K}(\vt_\ast, \{\vt_\ast \}^\textrm{grid}) & \mathcal{K}(\vt_\ast,\vt_\ast)
  \end{bmatrix}
  \right )
\end{equation}
where $\mathcal{K}( \{\vt_\ast \}^\textrm{grid}, \vt_\ast)$ represents a length-$M$ column vector 
evaluated pairwise with all values in $\{\vt_\ast \}^\textrm{grid}$ and the proposed value of 
$\vt_\ast$.  This vector is stacked horizontally next to $\mathbf{\Sigma}^\textrm{grid}$, and its 
transpose is stacked vertically underneath $\mathbf{\Sigma}^\textrm{grid}$.  The combination of all 
these products results in an augmented covariance matrix of size ($M + 1, M + 1$).  The probability 
distribution of $w_k(\vt_\ast)$ is given by the conditional Gaussian distribution 
\citep{rasmussen05}
\begin{equation}
  p(w_k |\; \{\vt_\ast \}^\textrm{grid}, \mathbf{w}_k^\textrm{grid}, \vt_\ast) =  \mathcal{N} \left ( w_k \Bigl | \Bigr . \,  \mu_k , \sigma_k \right ),
 \label{eqn:conditional_gp}
\end{equation}
where
\begin{equation}
 \mu_k =   \mathcal{K}(\vt_\ast, \{\vt_\ast \}^\textrm{grid}) (\mathbf{\Sigma}^{\textrm{grid}})^{-1} \mathbf{w}_k^\textrm{grid}
\end{equation}
and 
\begin{eqnarray}
  \sigma_k &=& \mathcal{K}(\vt_\ast,\vt_\ast) - \\
  & & \mathcal{K}(\vt_\ast, \{\vt_\ast \}^\textrm{grid}) (\mathbf{\Sigma}^{\textrm{grid}})^{-1} \mathcal{K}( \{\vt_\ast \}^\textrm{grid}, \vt_\ast) \nonumber.
\end{eqnarray}
% Should one of these be transposed?

>>>>

\capstartfalse
\begin{deluxetable}{lr@{ $\pm$ }l|r@{ $\pm$ }l}[!b]
\tablecaption{\label{table:Kurucz}Inferred Parameters for WASP-14}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{{\sc CfA/Kurucz}} & \multicolumn{2}{c}{{\sc Phoenix}}}
\startdata
$T_{\rm eff}$ (K) & 6424     & 19                      &  6349   & 20        \\
$\log g$      & 4.29     & 0 (fixed)               &  4.29   & 0 (fixed) \\
$\Z$          & -0.26    & 0.01                    & -0.31  & 0.02     \\
$v \sin i$ ($\kms$)\tablenotemark{a}   & 4.47 & 0.06       &  5.09   & 0.06      \\
$v_z$ ($\kms$)        & -4.60    & 0.02                    & -4.86   & 0.02      \\
$\log \Omega$\tablenotemark{b} & -12.7180 & 0.0004 & -12.717 & 0.001 \\
$A_V$                          & 0        & 0 (fixed) & 0 & 0 (fixed)
\enddata
\tablenotetext{a}{Small differences in the rotational broadening between the two libraries are
expected, since they assume different micro- and macro-turbulence behavior in the stellar
atmospheres.}
\tablenotetext{b}{For the spectral emulator (Appendix~\ref{sec:Appendix}), the models are scaled to 
an average flux of unity, rather than flux at the stellar surface; the quoted values are unknown 
multiples of $R^2/d^2$.}
\tablecomments{The quoted values represent the ``best-fit", the peak of the marginal posterior 
distributions for each parameter.  The quoted uncertainties correspond to the 68.3\%\ 
($\sim$1\,$\sigma$) confidence intervals.  Expanded lists of the inferred values and uncertainties 
for all nuisance parameters are available electronically.}
\end{deluxetable}
\capstarttrue

@@

\begin{figure*}[!t]
  \begin{center}
  \includegraphics{figs/pca_reconstruct.pdf}
  \vspace{-0.6cm}
  \figcaption{ (\emph{top}) The mean spectrum, standard deviation spectrum, and five eigenspectra 
that form the basis of the \textsc{Phoenix} synthetic library used to model Gl~51, generated using 
a subset of the parameter-space most relevant for M dwarfs.  (\emph{bottom}) The original synthetic 
spectrum from the \textsc{Phoenix} library ($\vt_\ast = [T_\textrm{eff} = 3000\,\textrm{K}, \log g =
  5.0\,\textrm{dex}, \Z = 0.0\, \textrm{dex}]$) compared with a spectrum reconstructed from a linear 
combination of the derived eigenspectra using Eqn~\ref{eqn:reconstruct} (with the weights $w_k$ 
listed in the top panel figure).  \label{fig:pca_reconstruct}}
  \end{center}
\end{figure*}

@@

Now the Gaussian process is fully specified and can be used to predict the values of the weights at 
any arbitrary set of stellar parameters $\vt_\ast$ by considering them drawn from the joint 
distribution 
\begin{equation}
  \begin{bmatrix}
    \mathbf{w}_k^\textrm{grid}\\
    w_k
  \end{bmatrix} \sim
  \mathcal{N} \left (
  \mathbf{0},
  \begin{bmatrix}
  \mathbf{\Sigma}_k^\textrm{grid} & \mathcal{K}( \{\vt_\ast \}^\textrm{grid}, \vt_\ast) \\
  \mathcal{K}(\vt_\ast, \{\vt_\ast \}^\textrm{grid}) & \mathcal{K}(\vt_\ast,\vt_\ast)
  \end{bmatrix}
  \right )
\end{equation}
where $\mathcal{K}( \{\vt_\ast \}^\textrm{grid}, \vt_\ast)$ represents a length-$M$ column vector 
evaluated pairwise with all values in $\{\vt_\ast \}^\textrm{grid}$ and the proposed value of 
$\vt_\ast$.  This vector is stacked horizontally next to $\mathbf{\Sigma}^\textrm{grid}$, and its 
transpose is stacked vertically underneath $\mathbf{\Sigma}^\textrm{grid}$.  The combination of all 
these products results in an augmented covariance matrix of size ($M + 1, M + 1$).  The probability 
distribution of $w_k(\vt_\ast)$ is given by the conditional Gaussian distribution 
\citep{rasmussen05}
\begin{equation}
  p(w_k |\; \{\vt_\ast \}^\textrm{grid}, \mathbf{w}_k^\textrm{grid}, \vt_\ast) =  \mathcal{N} \left ( w_k \Bigl | \Bigr . \,  \mu_k , \sigma_k \right ),
 \label{eqn:conditional_gp}
\end{equation}
where
\begin{equation}
 \mu_k =   \mathcal{K}(\vt_\ast, \{\vt_\ast \}^\textrm{grid}) (\mathbf{\Sigma}^{\textrm{grid}})^{-1} \mathbf{w}_k^\textrm{grid}
\end{equation}
and 
\begin{eqnarray}
  \sigma_k &=& \mathcal{K}(\vt_\ast,\vt_\ast) - \\
  & & \mathcal{K}(\vt_\ast, \{\vt_\ast \}^\textrm{grid}) (\mathbf{\Sigma}^{\textrm{grid}})^{-1} \mathcal{K}( \{\vt_\ast \}^\textrm{grid}, \vt_\ast) \nonumber.
\end{eqnarray}
